### 2020-08-14 code/survival/survfig.Rmd
Updates survival plots with new color scheme + key

p1 = ggplot(data.frame(r=patientsurvivalsbkd,c=patientsurvivalsk2,rm = mixedsurvwfk1, cm=mixedsurvwfk2, status=rep(1,length(patientsurvivalsbkd)))) +
geom_km(aes(time=r,status=status),color="blue") +
geom_km(aes(time=c,status=status),color="red") +
geom_km(aes(time=rm,status=status),color="darkblue") +
geom_km(aes(time=cm,status=status),color="darkred") +
annotate("text",rep(90,4),c(.9,.7,.5,.3),color=c("blue","red","darkblue","darkred"),label=c("Random 30 year old women","Random 30 year old women cancer k=2","Random uniform(30,70) year old women","Random uniform(30,70) year old women k=2"),hjust="right")+
labs(title="Simulated patients",x="Time (years)",y="Fraction Surviving")

@@

mytheme = theme(
#    axis.text.x = element_blank(),
#    axis.text.y = element_blank(),
    axis.title.x = element_text(size = 10),
    axis.title.y = element_text(size = 10),
#    axis.ticks = element_blank(),
#    axis.line = element_blank(),
    strip.text.y.right = element_text(angle = 0),
    strip.background = element_blank(),
    legend.position = "none",
    title = element_text(size=10)
  )

>>>>

p1 = data.frame(
    r = patientsurvivalsbkd,
    c = patientsurvivalsk2,
    rm = mixedsurvwfk1,
    cm = mixedsurvwfk2,
    status = rep(1, length(patientsurvivalsbkd))
) %>%
    rownames_to_column(var = "index") %>%
    pivot_longer(-c(index, status), values_to = "time", names_to = "condition") %>%
    ggplot(aes(time = time, color = condition, status = status)) +
    geom_km() +
    scale_color_manual(
        values = c(r = "#56b4e9", c = "#e69f00", rm = "#0072b2", cm = "#d55e00"),
        breaks = c("r", "c", "rm", "cm"),
        labels = c("Random 30 year old women", "Random 30 year old women cancer k=2", "Random uniform(30,70) year old women", "Random uniform(30,70) year old women k=2")
    ) +
    theme_classic() +
    theme(legend.position = c(.8, .75))

@@

mytheme = theme(
#    axis.text.x = element_blank(),
#    axis.text.y = element_blank(),
    axis.title.x = element_text(size = 10),
    axis.title.y = element_text(size = 10),
#    axis.ticks = element_blank(),
#    axis.line = element_blank(),
    strip.text.y.right = element_text(angle = 0),
    strip.background = element_blank(),
    legend.key.height = unit(0.4, "lines"),
    legend.title = element_blank(),
    #legend.position = "none",
    title = element_text(size=10)
  )
